article title

### 2022-07-08 article.tex
Add lists
Add definitions

@@

@@

\section{Bold, italics, and underline}
\label{sec:bold_italics_underline}
Bold text is done with \textbackslash{textbf\{\textless text \textgreater\}} such as \textbf{bolded text}.

@@

@@

@@

\subsubsection{Not started}
\label{sec:even_more_to_do}
matrices

@@

\section{Acknowledgement}
\label{sec:acknowledgement}

>>>>

% useful for definitions, theorems, corollaries, etc.
\theoremstyle{myenv}
\theoremstyle{mytheorem}
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{axiom}[theorem]{Axiom}
\theoremstyle{mydefinition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{exercise}[theorem]{Exercise}
\newtheorem{question}[theorem]{Question}
\newtheorem{problem}[theorem]{Problem}
\newtheorem{example}[theorem]{Example}
\newtheorem{remark}[theorem]{Remark}

% set no indent for lists
\usepackage{enumitem}
\setlist[itemize]{leftmargin=*}
\setlist[enumerate]{leftmargin=*}

@@

% create a list of definitions command
\newcommand{\listdefinitionsname}{List of Definitions}
\newlistof{mydefinitions}{def}{\listdefinitionsname}
\newcommand{\mydefinitions}[1]{%
\addcontentsline{def}{mydefinitions}{\protect\numberline{\thedefinition}#1}\par}
\renewcommand{\cftdeftitlefont}{\normalfont\Large\bfseries}

@@

\newpage
\section{Bold, italics, and underline}
\label{sec:bold_italics_underline}
Bold text is done with \textbackslash{textbf\{\textless text \textgreater\}} such as \textbf{bolded text}.

@@

\section{Lists}
Unordered list
\begin{itemize}
    \item Illinois
        \begin{itemize}
            \item Chicago
            \item Naperville
        \end{itemize}
    \item Kentucky
        \begin{itemize}
            \item Lexington
            \item Louisville
        \end{itemize}
\end{itemize}

Ordered list
\begin{enumerate}
    \item Cat
        \begin{enumerate}
            \item Persian
            \item Siamese
        \end{enumerate}
    \item Dog
        \begin{enumerate}
            \item Aussiedoodle
            \item Newfoundland
        \end{enumerate}
\end{enumerate}

@@

\section{Definitions}
\label{sec:definitions}

\begin{definition}[Definition of limit]
\label{def:limit}
Let $f$ be a function defined on an open interval containing $x=a$, but perhaps not at $x=a$.  We say $\displaystyle\lim_{x\to a}f(x)=L$ if for any $\epsilon>0$ there exists $\delta>0$ such that $|f(x)-L|<\epsilon$ whenever $0<|x-a|<\delta$.
\end{definition}
\mydefinitions{Definition of limit}

\begin{definition}
\label{def:derivative}
The \textit{derivative} of $f$ is defined to be $\displaystyle f^\prime(x)=\lim_{h\to 0}\frac{f(x+h)-f(x)}{h}$, if this limit exists.
\end{definition}
\mydefinitions{Derivative of f}

\section{Theorems}
\label{sec:theorems}

\begin{theorem}[Fundamental Theorem of Calculus]
\label{thm:ftc}
If $f$ is continuous on the interval $[a,b]$, then \[\frac{d}{dx}\int_a^x f(t)dx=f(x)\] for all $a\le x\le b$.
\end{theorem}

@@

\subsubsection{Not started}
\label{sec:even_more_to_do}
- matrices

@@

\newpage
\listofmydefinitions

\newpage
\section{Acknowledgement}
\label{sec:acknowledgement}
